\chapter{Installation}\label{installation}\index{Installation}%
\setheader{{\it CHAPTER \thechapter}}{}{}{\ctsimheadtitle}{}{{\it CHAPTER \thechapter}}%
\ctsimfooter%

\section{Download}\label{download}\index{Download}%

The latest version of \ctsim, both as executable programs and source code,
 can be downloaded from the official
 \ctsim\ \urlref{web site}{http://www.ctsim.org}. Additionally, these
 files are also available from the \ctsim\ \urlref{FTP site}{files://files.b9.com/ctsim}.


\section{Installing Windows Binary}

Download the Windows executable file.
Simply execute this program to begin the
installation program. \ctsim\ will then be accessible from the
\texttt{Start} Menu under the \texttt{Programs} submenu.

\ctsim\ is compatible with Windows 98, Windows Me, Windows NT 4.0,
and Windows 2000. Due to use of the OpenGL and htmlhelp libraries,
\ctsim\ is not compatible with the stock Windows 95 system.

\section{Installing Linux RPM}
Download the \ctsim\ RPM file, then use
the \texttt{rpm} manager program as follows:\\
\hspace*{1cm}\texttt{rpm -Uvh} \emph{ctsim-*.rpm}\\

\ctsim\ and \ctsimtext\ will then be installed in the \texttt{/usr/local/bin}
directory. The online help file, \texttt{ctsim.hhp}, will be installed in
directory \texttt{/usr/local/man}.

\section{Build From Sources}\label{build}\index{Source code build}

Refer to the INSTALL file included in the source distribution for
instructions.

\subsection{Optional Libraries}
These libraries are optional and not required to build \ctsim\ from source code.
However, they add functionality to \ctsim\ and there inclusion is recommended.

  \begin{itemize}
  \item \textbf{wxWindows 2.3}\\
  Used for the platform-independent graphical interface. The graphical version
  of \ctsim\ requires this library.\\
  \urlref{Web site}{http://www.wxwindows.org}

  \item \textbf{FFTW3}\\
    Used for fast Fourier transformations of projections and images.
    Without this library \ctsim\ will use slower, traditional Fourier transformations.\\
    \urlref{Web site}{http://www.fftw.org}

  \item \textbf{libpng}\\
        Used for PNG file export.\\
    \urlref{Web site}{http://www.libpng.org/pub/png/libpng.html}

  \item \textbf{zlib}\\
        Used for PNG file export.\\
    \urlref{Web site}{http://www.info-zip.org/pub/infozip/zlib/zlib_docs.html}

  \item \textbf{readline}\\
    Used for \ctsimtext\ interactive shell.\\
    \urlref{Web site}{http://www.gnu.org}

  \item \textbf{dmalloc}\\
    Used for debugging memory allocation.\\
    \urlref{Web site}{http://www.dmalloc.com}

  \item \textbf{ctn}\\
    DICOM library used to support import/export of DICOM files
    \urlref{Web site}{http://www.erl.wustl.edu/DICOM/ctn.html}

\end{itemize}
